Reproducibility in plant pathology: where do we stand and a way forward

### 2021-10-15 analysis/paper/paper.Rmd
Revise data and code heading
Load here and bayesplot for a new figure 1

```{r, setup, echo = FALSE, message=FALSE}
library("officer")
library("dplyr")
library("janitor")
library("flextable")
library("Reproducibility.in.Plant.Pathology")
library("tidyr")
library("DiagrammeR")
library("DiagrammeRsvg")
library("rsvg")
library("ggplot2")
library("patchwork")

@@

# Author Recommended Internet Resources

>>>>

```{r, setup, echo = FALSE, message=FALSE}
library("officer")
library("dplyr")
library("janitor")
library("here")
library("flextable")
library("Reproducibility.in.Plant.Pathology")
library("tidyr")
library("DiagrammeR")
library("DiagrammeRsvg")
library("rsvg")
library("ggplot2")
library("bayesplot")
library("patchwork")

@@

# Data and Code Availability
